### 2025-05-28 sec/evaluation.tex
[charts] created new chart and inserted into the paper

\subsection{Success Rate by Testcase}
\label{subsec:success_rate_by_test_case}

@@

>>>>

\subsection{Success Rate by Testcase}
To evaluate the system we used a sample of the Scigen dataset \cite{scigen_dataset_2021}.
Figure \ref{fig:success_rate_by_test_case} shows the results obtained for each test case.

\label{subsec:success_rate_by_test_case}

@@

We also aggregated the generated expression in three categories: aggregation, trends, quantitative (See Table \ref{tab:fluid_examples}).
Figure \ref{fig:success_rate_by_category} shows the results obtained in generating expression by categories.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\linewidth]{fig/success_rate_by_category}
    \caption{Success rate by testcases}\label{fig:success_rate_by_category}
\end{figure}
